Introduction

### 2015-07-21 dissertation/problems.tex
Zipf problems

Caching plays an important role in the Web architecture
\cite{webarch}, because previous responses may be reused to satisfy a
current request. However, there are many problems that need to be
solved to use it for SPARQL query evaluation:

>>>>

Moreover, an ambition of the Semantic Web is to deal well with
heterogeneous data, and it has been known for long \cite{1385469} that:

\begin{problem}
The distribution of data is often dominated by a power-law.
\end{problem}
However, 
\begin{problem}
The data distribution is often unknown to the query engine, and so,
following the principle of indifference, assumes uniform
distributions.
\end{problem}

Caching plays an important role in the Web architecture
\cite{Jacobs:04:AWW}, because previous responses may be reused to
satisfy a current request. However, there are many problems that need
to be solved to use it for SPARQL query evaluation:
